### 2015-04-18 usecase-combinatoric.tex
Started Python section.

\subsection{Combinatoric Names}
\label{sec:usecase-combinatoric}

\subsubsection{Gperftools packaging}

The gperftools tool from Google has gained popularity among some developers for
its high-performance thread-safe heap and its lite-weight profilers.
Unfortunately, two issues made it difficult to maintain gperftools installations
at LLNL.  First, gperftools is a C++ library.  Since C++ does not have standard
ABI it needs to be re-built with each compiler and compiler version.  Second,
building gperftools on atypical architectures (such as Blue Gene/Q) requires
patches and a complicated configure line that change with each compiler.  The
first issue motivated application developers to try and maintain their own builds
of gperftools that worked with their prefered compilers--a task that was made
difficult by the second issue.

Spack presented a solution to both problems.  Package administrators can use Spack to
easily maintain a central install of gperftools across the combinations of versions
and compilers.  Spack's gperftools package also serves as a central repository for
the knowledge of how to build gperftools on each platform and compiler combination.

\begin{figure}
\begin{minted}[linenos,
               numbersep=5pt,
			   fontsize=\scriptsize,
               frame=lines,
               framesep=2mm]{python}
patch("patch.gpeftools2.4_xlc", when="@2.4 %xlc")

@@

Figure~\ref{fig:gperftools} illustrates per-compiler and platform build rules with
a simplified version of the install routine for the gperftools tool (Spack's real
install routine for gperftools includes other compilers and more options per
compiler).  It applies a patch if gperftools 2.4 is built with the XLC compiler,
and it selects the correct configure line based on the current platform and compiler.

\subsubsection{{\tt mpileaks} packaging}
\todo{.5 page}
\begin{verbatim}
	- compiler x version x MPI x mpi version
\end{verbatim}

>>>>

\subsection{Combinatoric Naming}
\label{sec:usecase-combinatoric}
%\subsubsection{Gperftools and MPILeaks}

{\tt Gperftools} is a suite of tools from Google that has gained popularity among
developers for its high-performance thread-safe heap and its lightweight profilers.
Unfortunately, two issues made it difficult to maintain {\tt gperftools} installations
at LLNL.  First, {\tt gperftools} is a C++ library.  Since C++ does not have standard
ABI, it needs to be re-built with each compiler and compiler version used by client
code.  Second, building {\tt gperftools} on bleeding-edge architectures
(such as Blue Gene/Q) requires patches and a complicated configure lines that
change with each compiler.  An LLNL application team tried to maintain their own
builds of {\tt gperftools} that worked with their preferred compilers, but this
task was complicated by the second issue.

Spack presented a solution to both problems.  Package administrators can use Spack to
easily maintain a central install of {\tt gperftools} across the combinations of
versions and compilers.  Spack's {\tt gperftools} package also serves as a central
institutional knowledge repository for builds, as its package files encode
the {\tt gperftools} patches and configure line for each platform and compiler combination.
We are investigating whether we can move some of these settings into compiler and
architecture descriptors to further simplify Spack's build template for cross-platform
installations.
\begin{figure}
\begin{minted}[linenos,
               numbersep=5pt,
			   fontsize=\scriptsize,
               frame=lines,
               framesep=2mm]{python}
patch("patch.gpeftools2.4_xlc", when="@2.4 %xlc")

@@

Figure~\ref{fig:gperftools} illustrates per-compiler and platform build rules with
a simplified version of the install routine for {\tt gperftools} (The full
{\tt gperftools} install routine includes other compilers and more options).  It applies a patch if {\tt gperftools} 2.4 is built with the XL compiler,
and it selects the correct configure line based on the spec's platform and compiler.

LLNL's {\tt mpileaks} tool, which we have used as a running example in this paper,
has an even larger configuration space than {\tt gperftools}.  It must be built
for different compilers, compiler versions, MPI implementations, and MPI implementation
versions. As with {\tt gperftools}, we have been able to install many different
configurations of MPILeaks using Spack.  Moreover, Spack's virtual dependency system
allows us to
quickly compose a new MPILeaks build when a new MPI is deployed at LLNL, {\it without}
modifying the MPILeaks package itself. Though we simplified its dependency structure
here, the {\tt callpath} library can be built with three different stack trace libraries:
{\tt dyninst}, {\tt libunwind}, or {\tt glibc}.  For some codes we may soon need to build
different versions of MPILeaks with different {\tt callpath} configurations.

### 2015-04-18 usecase-python.tex
Started Python section.

>>>>

Python is becoming increasingly popular for HPC applications, 
both due to its flexibility as a language and due to its excellent support
for calling into native numerical code and achieving high performance. 
Python applications frequently make native calls into functions in
compiled numerical libraries like NumPy, FFTW, ATLAS, and other linear
algebra libraries.

LC maintains a number of Python installations for production application teams,
and maintenance of these repositories has been increasingly complex for
some time.  LC must maintain different Python installations containing different
versions of Python modules for different code teams, and the modules must be able
to make calls into optimized native libraries, for maximum performance.
Python itself was easy to package with Spack; we built a package for it like any
other and it compiled and ran

they must also call into high performance math libraries. Python installations
suffer from many of the environment problems we mentioned in Sections~\ref{env-rpath}.

Python

 \cite{eby:setuptools}

Python's package management

To support code teams using Python, LC maintains a number of

both for rapid prototyping

- LC maintains python installations for existing codes.

- maintain separate instances for different code teams
	- each code team needs to have particular python packages installed
	- need fast builds of math libraries to go with python installs

- model for python package installation doesn't really fit spack

- implemented best of both worlds solution:
	- combine spack's flexibility with python meta-package-manager convenience

	- many other languages fit this model; could use it w/them.

### 2015-04-18 usecases.tex
flow.
Started Python section.

>>>>

We have recently using Spack in production at 
Livermore Computing.  We have already outlined a number of the
experiences that drove us to develop Spack.
In this section, we describe real-world use cases that Spack
has been used to address.  In some cases, Spack had to be 
adapted to meet production needs, and we describe how its
flexibility has allowed us to put together solutions quickly.
